Untitled

### 2021-05-04 output/forecast_plots.Rmd
Fix problem with lower CI values below zero; fix Rmd headings

  forecasts %>% 
    filter(incident_type_new %in% types) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, actual_calls)) +
    geom_point(aes(incident_week, actual_calls, fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y") +
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = "Calls for service during 2021 compared to pre-pandemic forecast",
      subtitle = str_wrap(
        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
        80
      ),
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = "weekly count of calls for service",
      fill = "actual calls significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

@@

#Abondended Phone Call

@@

#Admin

@@

#Alarms

@@

#Widlife Concern

@@

#ASB

@@

#Burglary - Commercial

@@

#Burglary - Residential

@@

#Civil Disputes

@@

#Police Safety

@@

#Minor Injuries

@@

#Complaints Against Police

@@

#Concern for Safety

@@

#Criminal Damage

@@

#Distraction Burglary

@@

#Domestic Incident

@@

#Drug Related Offences

@@

#Firearms

@@

#Fraud

@@

#Hate Incident

@@

#Highway Disruption

@@

#Missing Person

@@

#Other - Admin Calls

@@

#Other - minor

@@

#Police Generated

@@

#Potential Breach of the Peace

@@

#Property Lost/Found

@@

#Road Related Traffic Offence

@@

#Robbery

@@

#Sexual Offences

@@

#Shoplifitng

@@

#Sudden Death

@@

#Suspicious Activity

@@

#Suspicious Package

@@

#Theft from Motor Vehicle

@@

#Theft of Motor Vehicle

@@

#Theft Other

@@

#Traffic collision

@@

#Violence and Harassment Incidents

@@

#Warrant and Bail Incidents

>>>>

  forecasts %>% 
    filter(incident_type_new %in% types) %>% 
    # Occasionally the ARIMA model may produce forecast confidence intervals
    # that are less than zero, which will not show up on the plot because we
    # have set the y axis to start at zero (to make changes in vertical position
    # on the axis representative of changes in magnitude). To deal with this we
    # will manually set the lower CI of the forecasts to be zero if it is less
    # than zero in the original forecast.
    mutate(forecast_lower = ifelse(forecast_lower < 0, 0, forecast_lower)) %>% 
    ggplot() +
    # Forecast
    geom_ribbon(
      aes(incident_week, ymin = forecast_lower, ymax = forecast_upper), 
      na.rm = TRUE,
      alpha = 0.5, 
      fill = "grey80"
    ) +
    geom_line(aes(incident_week, forecast_mean), na.rm = TRUE, linetype = "22") +
    # Dates of interest
    geom_vline(aes(xintercept = date), data = dates, linetype = "12") +
    geom_label(aes(date, 0, label = row), data = dates, colour = "grey20") +
    # Actual calls
    geom_line(aes(incident_week, actual_calls)) +
    geom_point(aes(incident_week, actual_calls, fill = sig), shape = 21) +
    scale_x_date(date_labels = "%e %b\n%Y") +
    scale_y_continuous(limits = c(0, NA), labels = scales::comma_format()) +
    scale_fill_manual(values = c(`TRUE` = "black", `FALSE` = "grey80")) +
    labs(
      title = "Calls for service during 2021 compared to pre-pandemic forecast",
      subtitle = str_wrap(
        str_glue("Events by week: ", str_c(pull(dates, label), collapse = "; ")), 
        80
      ),
      caption = "Forecast calculated using data up to 31 January 2020",
      x = NULL,
      y = "weekly count of calls for service",
      fill = "actual calls significantly different from forecast"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom", plot.title = element_text(face = "bold"))

@@

## Abondended Phone Call

@@

## Admin

@@

## Alarms

@@

## Widlife Concern

@@

## ASB

@@

## Burglary - Commercial

@@

## Burglary - Residential

@@

## Civil Disputes

@@

## Police Safety

@@

## Minor Injuries

@@

## Complaints Against Police

@@

## Concern for Safety

@@

## Criminal Damage

@@

## Distraction Burglary

@@

## Domestic Incident

@@

## Drug Related Offences

@@

## Firearms

@@

## Fraud

@@

## Hate Incident

@@

## Highway Disruption

@@

## Missing Person

@@

## Other - Admin Calls

@@

## Other - minor

@@

## Police Generated

@@

## Potential Breach of the Peace

@@

## Property Lost/Found

@@

## Road Related Traffic Offence

@@

## Robbery

@@

## Sexual Offences

@@

## Shoplifitng

@@

## Sudden Death

@@

## Suspicious Activity

@@

## Suspicious Package

@@

## Theft from Motor Vehicle

@@

## Theft of Motor Vehicle

@@

## Theft Other

@@

## Traffic collision

@@

## Violence and Harassment Incidents

@@

## Warrant and Bail Incidents
